Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2024-03-26 introduction_new.tex
Updates from Overleaf

Prevalence surveys designed to draw random samples from the population are one form of prevalence-type data that can be unbiased.
Here, a representative proportion of the population (or a sub-population of interest) are tested for a marker of current infection.
For many diseases, prevalence is sufficiently low that this is prohibitively expensive to power.

>>>>

Prevalence surveys designed to draw random samples from the population are one source of prevalence-type data that can be unbiased.
For instance, a representative proportion of the population (or a sub-population of interest) are tested for a marker of current infection.
For many diseases, prevalence is sufficiently low that this is prohibitively expensive to power.
